---
title: "HW2_d06521014"
author: "d06521014@ntu.edu.tw"
date: "2017年10月3日"
output: html_document
---
#HW2 Airplane Crashes Since 1908
Analysis of the "Airplane Crashes and Fatalities Since 1908"  dataset(source:https://opendata.socrata.com/Government/Airplane-Crashes-and-Fatalities-Since-1908/q2te-8cvq)
The main purpose of this homework is to practice dypler package of R, including 'filter', 'select','mutate', 'arrange', summarise, and group_by. On the other hand, tring to find any interesting trends or behaviors  when analyzing the dataset.

##Import data and View data

```{r eval=TRUE}
library(dplyr)
library(ggplot2)
library(gridExtra)
```
```{r}
crashdata<- read.csv("Airplane_Crashes_and_Fatalities_Since_1908.csv", header=T, sep=",")
dim(crashdata)
str(crashdata)
```
##Import data and View data
###Q1:the planes crashed each month


```{r}
#Date sturcture is mm/dd/yyyy
crashdata$year<-substr(crashdata$Date, start =7 , stop =10 )
crashdata$month<-as.factor(substr(crashdata$Date, start =1 , stop =2 ))
crashdata$day<-substr(crashdata$Date, start =4 , stop =5)

#death events in each month
death_month<-
  crashdata%>%
  group_by(month)%>%
  summarise(cumulative_number=n())
ggplot(death_month, aes(x=month,y=cumulative_number)) + 
  geom_bar(stat="identity")+
  geom_text(aes(label=cumulative_number),vjust=1.5,colour="white")
```

其中456月較低，但發生空難次數各月並沒有顯著的差別。

###Q2:the planes crashed per year
###Q3:people aboard per year during crashes
###Q4:people dead per year during crashes
###Q5:people survived rate per year during crashes
```{r}
#death events in each year
death_year<-
  crashdata%>%
  select(year,Aboard,Fatalities)%>%
  group_by(year)%>%
  na.omit()%>%
  summarise(events_number=n(),aboard=sum(Aboard),fatalities=sum(Fatalities),survival=sum(Aboard)-sum(Fatalities))

death_year$year<-as.integer(death_year$year)
death_year$survival_rate<-death_year$survival/death_year$aboard
g1<-ggplot(death_year, aes(year,events_number)) + 
  geom_line()+
  ggtitle("number of events")+
  theme(plot.title=element_text(vjust=-1.5))+
  theme(axis.title.x=element_blank())
g2<-ggplot(death_year, aes(year,aboard)) + 
  geom_line()+
  ggtitle("aboard ")+
            theme(plot.title=element_text(vjust=-1.5))+
  theme(axis.title.x=element_blank())
g3<-ggplot(death_year, aes(year,fatalities)) + 
  geom_line()+
  ggtitle("fatalities" )+
            theme(plot.title=element_text(vjust=-1.5))+
  theme(axis.title.x=element_blank())
g4<-ggplot(death_year, aes(year,survival_rate)) + 
  geom_line()+
  ggtitle("survival_rate")+
  theme(plot.title=element_text(vjust=-1.5))+
  theme(axis.title.x=element_blank())
grid.arrange(g1, g2,g3,g4,nrow = 4)

```

就年度來看，空難次數由1908年起開始隨時間增加，到約1973年達到最高峰，但2000年以後亦逐步下降。
猜測1908年起增加係因飛機數量增加，飛航的總次數亦增加，但資料目前欠缺飛航的總次數，無法佐證。
空難的登機人數、死亡人數和空難次數大致有一致的趨勢。
但在死亡率部份，反到1998年最高，近年來亦無減少的態勢，可見，時代進步亦無法降低空難之死亡率。

###Q6:Airlines to avoid
```{r}
death_operator<-
  crashdata%>%
  filter(Fatalities>1& !is.na(crashdata$Operator) )%>%
  select(Operator,Aboard,Fatalities)%>%
  group_by(Operator)%>%
  na.omit()%>%
  summarise(cumulative_number=n(),fatalities=sum(Fatalities))%>%
  arrange(desc(fatalities))
death_operator_top<-head(death_operator,5)

ggplot(death_operator_top, aes(x=Operator,y=fatalities)) + 
  geom_bar(stat="identity")+
  geom_text(aes(label=fatalities),vjust=1.5,colour="white")
```
因為太多家航空公司會無法聚焦，直接用head函數取前5名的航空公司，
Aeroflot 俄羅斯航空公開股份公司，簡稱俄航，是俄羅斯的國家航空公司
Military - U.S. Air Force
Air France 美國空軍
American Airlines 美國航空
Pan American World Airways 泛美航空
前5間最常發生空難公司有4間是美國，一間是俄羅斯

###Q6:問題請教 本來還有進行空難地點分析
```{r}
death_location_tmp<-
  crashdata%>%
  select(Location,Aboard,Fatalities)%>%
  group_by(Location)%>%
  na.omit()
x<-strsplit(as.character(death_location_tmp$Location), split = ",")
x[[1]]
tail(x[[1]],1)

for (i in 1:length(death_location_tmp)){
  death_location_tmp$location[i]<-tail(x[[i]],1)
}
#此處出現問題，想把death_location_tmp取,後的字，但無法成功

death_location<-death_location_tmp%>%
  group_by(location)%>%
  summarise(cumulative_number=n(),fatalities=sum(Fatalities))%>%
  arrange(desc(fatalities))
  
 death_location_top<- head(death_location,5)
 ggplot(death_location_top, aes(x=location,y=fatalities)) + 
  geom_bar(stat="identity")+
  geom_text(aes(label=fatalities),vjust=1.5,colour="white")
 
```

